JLyrics \titlenote{Submitted as the final project for CS 410 Summer 2014.}

### 2014-08-03 report/paper.tex
Report: Piapro doc creation, bibliography, image for results.

In order to parse each of these HTML files, since the characters were in UTF-8, a setlocale was required. Also, the glibmm library provides wrappers for processing UTF-8 strings with the Glib::ustring data type, which can be used much in the same way as the std::string data type. It also provides a regex library for UTF-8 regular expressions. As the pages were downloaded, each line was checked for matching regular expressions. The following regular expressions were used:

\begin{itemize}
 \item (?<=/t/).\{4\} : Used to match song links because all songs had a four character id under the /t/ directory.
 \item (?<=「).*(?=」) : Used to match the title on the song page, since they were contained in the square open quote.
 \item (?<=$''$/).*?(?=$''$ class=$''$i\_icon) : Used to match the user name, since it always followed the tag with i\_icon in it.
 \item p id=$''$\_txt\_main$''$ : Used to find the first line of lyrics, which had a different pattern in the html document.
 \item (?<=>).*(?=<br) : Used to match the first line of lyrics
 \item \^{}.+(?=<br) : Used to match all other lyrics, each of which had a line break tag after it.
 \item \^{}.*(?=</p) : Used to match the last line of lyrics, which breaks out of the processing loop.
\end{itemize}

Just for convenience, a progress checker that kept track of the number of songs was introduced. Furthermore, a time delay was used to prevent too many requests being sent at once. This was a small random integer of seconds.

Due to the sheer number of songs to crawl, it became necessary to distribute the processing over a number of computers. Another issue was that EWS lacks the required libraries to compile this code or even run the executable. As a result, a simplification needed to be made. This time, the crawler simply took the html files, so that they could all be processed on a machine with the required library files. In short, the original crawler was split into two parts. As a result, the following scheme was used: (Note: Ideally, the number of links would have been 141,303, but due to the site being updated, there were duplicate links.)

@@

Assuming an up-to-date system as of July 31, 2014, the following libraries were used in the first crawler: (Note: the split up crawler uses a combination of these.)

\begin{itemize}
 \item glibmm/ustring.h : ustring data type and functions
 \item glibmm/regex.h : UTF-8 regex library
 \item libxml++ : required to use the above two
 \item iostream : streams
 \item cstdio : popen function (used to count lines in the linkFile)
 \item clocale : Set to UTF-8 mode
 \item fstream : fileio
 \item string : std::string for line-by-line reading
 \item sstream : string concatenation
 \item cstdlib : system() function, random() function
 \item ctime : seeds random()
 \item thread : sleep\_for() function
 \item chrono : provides sleep\_for with number of seconds.
\end{itemize}

Compilation commands (Makefile):

\begin{itemize}
 \item Zach's laptop: g++ -g -std=c++0x main.cpp -o main `pkg-config libxml++-2.6 --cflags glib-2.0 --libs glib-2.0`
 \item EWS machines (crawl): g++ -g -std=gnu++0x main.cpp -o main -D\_GLIBCXX\_USE\_NANOSLEEP
 \item Zach's laptop (after EWS crawl): g++ -g -std=c++0x postParse.cpp -o postParse `pkg-config libxml++-2.6 --cflags glib-2.0 --libs glib-2.0`
\end{itemize}

@@

@@

@@

Firstly, we think that the creation of a webpage would have been a nice addition to the project. To give a more concrete idea, certain websites have a built-in custom search bar and display search results in the browser. This would be a big advantage over the command line searcher because command line applications requires special knowledge of the command line and terminal applications can't handle Japanese characters if the font does not support the proper size of the characters (backspacing disaligns the cursor).

@@

\bibliographystyle{plain}
\bibliography{bib} % "bib" is the name of the .bib file

>>>>

Just for convenience, a progress checker that kept track of the number of songs was added. Furthermore, a time delay was used to prevent too many requests being sent at once. This was a small random integer of seconds.

Due to the sheer number of songs to crawl, it became necessary to distribute the processing over a number of computers. Another issue was that EWS lacks the required libraries to compile this code or even run the executable. As a result, a simplification needed to be made. This time, the crawler simply took the HTML files, so that they could all be processed on a machine with the required library files. In short, the original crawler was split into two parts. As a result, the following scheme was used: (Note: Ideally, the number of links would have been 141,303, but due to the site being updated, there were duplicate links.)

@@

@@

In order to parse each of these HTML files, since the characters were in UTF-8, a setlocale() was required. Also, the glibmm library provides wrappers for processing UTF-8 strings with the Glib::ustring data type, which can be used much in the same way as the std::string data type. It also provides a regex library for UTF-8 regular expressions. As the pages were downloaded, each line was checked for matching regular expressions.

The C++ code made extensive use of lookaheads and lookbehinds to facilitate writing directly to the documents. These were determined by observation of the HTML pages.

@@

After indexing all of these documents with Goose, we performed a search using the -{}-search option. As shown in Figure~\ref{fig:res/410_post_Piapro.png}, a search for the first line of the lyrics of ``Hare Hare Yukai'' yielded good results.

\Figure[caption={Successful Search Example}]{res/410_post_Piapro.png}

@@

Firstly, we think that the creation of a webpage would have been a nice addition to the project. To give a more concrete idea, certain websites have a built-in custom search bar and display search results in the browser. This would be a big advantage over the command line searcher because command line applications requires special knowledge of the command line and terminal applications can't handle Japanese characters if the font does not support the proper size of the characters (backspacing misaligns the cursor).

@@

%\bibliographystyle{plain}
%\bibliography{bib} % "bib" is the name of the .bib file
